\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-04-14 doc/sw-system.tex

We describe \SW, a novel gravitaional lens discovery service that
yields samples of high purity and completeness through crowd-sourced
visual inspection.
Carefully
produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates; this ``\StageOne'' set is then re-classified
by the volunteers in a second  refinement stage. Analyzing the classification
of the training set, we predict that the first stage alone should yield a
sample that is C\% complete, while leading to the rejection of R\% of the
initial target sample. Having divided the 150 square degree CFHTLS imaging
survey into 430000 overlapping 84 by 84 arcminute tiles and displayed them on
the site, we were joined by 33000 volunteers who contributed X million image
classifications over the course of N months. The sample was reduced to 3500
\StageOne candidates; these were then refined to yield a sample of 1400
candidates rankable by their \StageTwo probability. We expect this sample to be
X\% complete and Y\% pure at a threshold of 95\% classification probability.
We find that, on average, and given the assumptions we make in our analysis,
we need 9 classifications per image during the first stage, X in the second.
We estimate the mean information contributed per person to be X bits, over a
session lasting, on average, N classifications per volunteer, and present the
highly skewed distributions of these quantities. We comment on the scalability
of the \SW system to the wide field survey era, and its potential to operate
beyond its design as a supervised classification system.

\todo{Phil}{revisit abstract (\#29).}

>>>>

We describe \SW, a novel gravitaional lens discovery service that yields samples
of high purity and completeness through crowd-sourced visual inspection.
Carefully produced color composite images are displayed to volunteers via a
classification interface which records their estimates of the positions of
candidate lensed features. Simulated lenses, and expert-classified non-lenses,
are inserted into the image stream at random intervals; this training set is
used to give the volunteers feedback on their performance, and to estimate a
dynamically-updated probability for any given image to contain a lens. Low
probability systems are retired from the site periodically, concentrating the
sample towards a set of candidates. Having divided the 171 square degree CFHTLS
imaging survey into some 430,000 overlapping 84 by 84 arcminute tiles and
displayed them on the site, we were joined by around 37,000 volunteers who
contributed 10 million image classifications over the course of 8 months. The
sample was reduced to 3300 \StageOne candidates; these were then refined to
yield a sample of 90 \StageTwo detections, a sample we expect to be over 90\%
complete and 20\% pure at a threshold of 95\% classification probability. We
comment on the scalability of the \SW system to the wide field survey era.
